---
title: "introduction2binomial"
author: "Wei Le"
date: "'r Sys.Date()'"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction2binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

## Introduction to Binomial
The package '"binomial"' is a minimal implementation for calculating probabillities of a Binomial random variable, and related calculations such as probability distribution, the expected value, variance, etc.

## bin_choose function
This is a trivial function which is eequivalent to choose k from n.

```{r}
bin_choose(5,2)
```
## bin_mean function
This is a simple function returns the expected value of successes for n trials with probability p.


```{r}
bin_mean(10,0.5)
```

## bin_mode function
This is a simple function returns the most likely  number of success in n independent trials with probability p of success on each trial is m, the greater integer less than or equal to np+p.

```{r}
bin_mode(11,0.6)
```
## bin_variance function
This is a simple function depicts the variance of given n and p, returns np(1-p).

```{r}
bin_variance(10,0.5)
```

## bin_skewness function
This is another simple function measuring the asymmetry of the probability distribution of a random variable about its mean.

```{r}
bin_skewness(10,0.5)
```

## bin_kurtosis function
This is a function measuring the "tailedness" of the probability distribution of a random variable.

```{r}
bin_kurtosis(10,0.5)
```

## bin_probability function
This is a function measuring the expected probability of given wanted successes and prob p and trials n.

```{r}
bin_probability(10,20,0.5)
```

## bin_distribution function
You can use this function to see the distribution of bin_probability for any successes given prob p and trials n.
Additionally, you can visualize the table via the supported function plot().

```{r}
temp<-bin_distribution(20,0.5)
temp
plot(temp)
```

## bin_cumulative function
You can use this function to get the cumulative table of bin_distributions.
Also, plot it to visualize.

```{r}
temp<-bin_cumulative(10,0.5)
temp
plot(temp)
```
## bin_variable function
This is the final summary function for this package which gives you the total summary of the variables.
By summarizing  it, you can get the trials and prob data; also, by depicting the summary gives you the mean, mode, variance, skewness, and kurtosis of the given prob and trials.

```{r}
bin1<-bin_variable(trials=10,p=0.3)
bin1

binsum1<-summary(bin1)
binsum1
```

